\index{Chicken!Adobo}
\begin{recipe}{Chicken Adobo}{Serves Four}{}
\freeform The national dish of the Philippines. Adapted from Purple Yam Restaurant in Brooklyn by Sam Sifton of the NYTimes. We like to serve it over brown rice.\\
\rule{\textwidth}{0.05pt}

\ing[1\fr12]{c}{rice vinegar}
\ing[1]{c}{coconut milk}
\ing[\fr14]{c}{soy sauce}
\ing[12]{cloves}{peeled garlic}
\ing[1-2]{}{Thai hot peppers or a jalapeno, halved and seeded}
\ing[3]{}{bay leaves}
\ing[1\fr12]{tsp}{freshly ground black pepper}
\ing[3-4]{lbs}{chicken thighs}

Combine all of the marinade ingredients in a large, nonreactive bowl
or resealable plastic freezer bag. Add the chicken and turn to
coat. Refrigerate overnight or for at least 2 hours.

\freeform Place chicken and marinade in a large lidded pot or Dutch
oven over high heat and bring to a boil. Immediately reduce heat to a
simmer and cook, stirring occasionally, until the chicken is cooked
through and tender, around 30 minutes.  Heat broiler. Transfer chicken
pieces to a large bowl, raise heat under the pot to medium-high, and
reduce the sauce until it achieves almost the consistency of cream,
about 10 minutes. Remove bay leaves and hot peppers.  Place chicken pieces
on a roasting pan and place under broiler for 5 to 7 minutes, until
they begin to caramelize. Remove, turn chicken, baste with sauce and
repeat, 3 to 5 minutes more. Return chicken to sauce and cook for a
few minutes more, then place on a platter and drizzle heavily with
sauce.
\end{recipe}
