\index{Stews!Garbanzos and Spinach}
\begin{recipe}{Garbanzos con Espinacas}{Serves 2 - 3}{1\fr12 hours}
\freeform
Spanish Chickpea and Spinach Stew with Ginger. From Serious Eats. This recipe happens to be vegan, but we don't hold that against it. Serve over brown rice.\\
\rule{\textwidth}{0.05pt}

\ing[1]{28 oz can}{ whole peeled tomatoes}
\ing[1]{1 inch knob}{ginger, peeled}

Drain tomatoes in a metal strainer set over a medium bowl. Transfer liquid and half of tomatoes to a blender along with ginger. Blend on high speed until completely pureed. Set aside. Roughly chop remaining peeled tomatoes and set aside separately.
\newline
\ing[\fr14]{cup}{extra-virgin olive oil}
\ing[1]{}{medium onion, finely sliced}
\ing[4]{cloves}{garlic, finely sliced}
\ing[1]{tsp}{sweet or hot smoked paprika}
\ing[12]{ounces}{fresh spinach, roughly chopped}

Heat olive oil in a large straight-sided skillet over high heat until shimmering. Add onion, garlic, and paprika, and cook, stirring frequently, until softened and very slightly browned. Add tomato-ginger puree (it should immediately start simmering) and stir to combine. Add spinach a handful at a time, allowing each handful to wilt before adding the next. Reduce heat to medium and allow spinach mixture to simmer, stirring occasionally, until spinach is completely tender, about 10 minutes.
\newline
\ing[2]{cans}{chickpeas}
\ing[2]{}{bay leaves}
\ing[2]{tsp}{soy sauce}

Add chopped tomatoes, garbanzo beans (with their liquid) bay leaves, and soy sauce, and bring to a boil over high heat. Reduce to a bare simmer and cook, stirring occasionally, until thickened into a thick stew, about 30 minutes total.
\newline
\ing[]{}{kosher salt}
\ing[]{}{sherry vinegar for serving (optional)}

Season to taste with kosher salt and serve immediately, drizzling with extra virgin olive oil and a a few drops of sherry vinegar.

\end{recipe}
