\index{Pie!Lemon Meringue}
\begin{recipe}{Lemon Meringue Pie}{}{}
\freeform
This recipe, better known in our house as LMNOP, is a Margie Goldberg
classic. Originally from the James Beard Cookbook, it's a bit of a
challenge, but well worthwhile.\\
\rule{\textwidth}{0.05pt}

\ing[1]{large}{egg yolk}
\ing[2]{tbsp}{ice water}
\ing[1]{tbsp}{lemon juice}
\ing[1]{pinch}{salt}
\ing[1]{stick}{butter}
\ing[1\fr12]{c}{AP flour}
\ing[2]{tbsp}{sugar}

\textbf{The Pastry}\\
Beat yolk lightly and add ice water, lemon juice, and salt. Cut or
work butter into flour, then add, along with sugar, to the egg
mixture. Work ingredients together until they form a soft ball. Chill
for \fr12 hour and pat into a flan ring or 9-inch tin. Place a piece
of foil inside shell and fill with pie weights. Bake at 350 for 25 to
30 minutes. Remove weights.


\ing[6]{}{egg yolks}
\ing[1\fr12]{c}{sugar}
\ing[1]{}{grated lemon rind}
\ing[\fr12]{c}{lemon juice}
\ing[3]{tbsp}{butter}
\ing[4]{tbsp}{cornstarch}
\ing[\fr14]{tsp}{salt}
\ing[1\fr12]{c}{boiling water}

\textbf{The Filling}\\
Beat egg yolks well, add remaining ingredients except boiling water,
and beat again thoroughly. Combine with boiling water and pour into
top of double boiler. Cook over hot water till mixture thickens, and
allow to cook for 5 to 10 minutes longer over simmering water. Pour
into baked shell. Top with meringue.

\ing[3]{}{egg whites}
\ing[1]{tsp}{cream of tartar}
\ing[1]{pinch}{salt}
\ing[6]{tbsp}{sugar}

\textbf{The Meringue}\\
Beat egg whites till they form soft peaks. Add cream of tartar and
salt and continue beating till whites are stiff but not dry. Add
sugar, a little at a time, beating it in well. Spread meringue over
the pie, being certain to cover the surface completely, including the
edge of the crust. If you are deft with the pastry tube, you may pipe
the meringue over the pie, using a number 6 rosette tube. Bake the
meringue at 350 for 15 to 18 minutes, or until it is lightly browned.

\end{recipe}
