\index{Quiche!Kester's Crustless}
\begin{recipe}{Kester's Crustless Quiche}
{\unit[6]{servings}}{\unit[1\fr14]{hours}}

\freeform This recipe came from Annie Kester. Annie and Joe Kester have been
friends of ours since within a year after arriving in Madison. Their daughter
Olive met our daughter Annie at Bridges Daycare. Since then their son
Lee and Stuart have become friends too. This is a great dish for
family brunch. Preheat oven to \unit[350\0]{F.} Butter a \unit[9]{in.}\
pie pan.

\ing[2]{cups}{chopped veggies/meat}
\ing[a few]{tbsp.}{butter}
Saute veggies/meat in butter. Add to the pie pan.
\ing[6]{oz}{cheese, shredded, Swiss or cheddar, medium firmness}
Add cheese on top of the veggies/meat. (\unit[1\fr12]{cups} or \unit[6]{oz}?)
\ing[6]{}{eggs}
\ing[1 \fr12]{cups}{heavy cream}
\ing[\fr12]{tsp}{salt}
\ing[\fr14]{tsp}{black pepper}
Whisk together eggs, cream, salt, and pepper. Pour egg mixture over
the cheese and veggies/meat.
\freeform Bake 50 minutes until eggs are set and top is
slightly brown.  Remove from oven and let stand 5 minutes before
cutting.\\\\
``I made it yesterday and it turned out great. I swapped half
and half for the heavy cream and it set fine. I think I put too much
cheese in because I couldn't fit the entire amount of egg mixture in
the pie pan, either that or a deep dish pie pan would have been
better. I made broccoli, onion, and cheddar since that's what we had
around, I love how versatile it is. Thanks again for sharing!'' - Sarah Goldberg, August 1, 2024
\end{recipe}
%garlic powder, ground mustard,  ground nutmeg...
