\index{Dumplings!Shu Mai}
\begin{recipe}{Shrimp and Cilantro Shu Mai}{Yield 10 to 12 dumplings}{30 minutes}
\freeform Not sure where we found this recipe, but we've had fun with it, especially for make-your-own dumpling kids' birthday parties. If you've got some bamboo steamers, you can do multiple levels at once. Parchment steamer liners keep dumplings from sticking. A steaming ring lets you place everything over a stock pot.\\
\rule{\textwidth}{0.05pt}

\ing[\fr12]{c}{soy sauce}
\ing[1]{tbsp}{rice wine}
\ing[1]{tbsp}{sesame oil}
\ing[1]{tbsp}{minced fresh ginger}
Combine the soy sauce, rice wine, sesame oil, and ginger in a bowl.

\ing[\fr12]{pound}{shrimp, peeled and deveined}
\ing[\fr34]{c}{cilantro leaves}
\ing[\fr14]{c}{roughly chopped scallions, white parts only}
Put half the shrimp, half the cilantro, and all the scallions in a food processor and pulse; add just enough of the soy mixture to create a smooth paste, about 1 to 2 tablespoons. Transfer to a bowl. Roughly chop the remaining shrimp and cilantro, add them to the bowl and stir to combine.

\ing[10 to 12]{}{round dumpling skins}
Place a dumpling skin on a work surface, moisten the edges with water, and put 1 teaspoon of the filling in the center. Gather the edges of the wrapper up around the filling, squeezing gently, to pleat the sides; some of the filling should remain exposed. Repeat with the remaining dumpling skins and filling, keeping the dumpling wrappers and dumplings covered with damp towels while you work.

\ing[]{}{juice of 1 lime}
Rig a steamer in a large pot over an inch of water; bring to a boil and reduce to a simmer. Meanwhile, add the lime juice to the remaining soy mixture to make a dipping sauce.

\newstep
Put as many dumplings in the steamer as you can fit in a single layer and cover the pot. Cook until the exposed filling turns pink and the wrappers are tender, 4 to 6 minutes, then transfter the dumplings to a serving platter. Repeat with the remaining dumplings. Serve with the dipping sauce.

\end{recipe}