\index{Cookies!Chocolate Chip!Spiced Oatmeal}
\begin{recipe}{Spiced Oatmeal Chocolate Chip Cookies}{Yield 20 to 24 Cookies}{}
\freeform
From the Chocolate Bar Cookbook. Sarah and I reduced the sugar by 1/3
after hearing an inspirational NPR interview. I swear they taster
better this way - perhaps more savory. Oh, and we sprinkle them with
sea salt. Maldon's if you want to get real fancy.\\
\rule{\textwidth}{0.05pt}
\ing[1\fr34]{c}{unbleached flour}
\ing[1]{tsp}{baking soda}
\ing[1]{tsp}{salt}
\ing[1]{tsp}{ground cinnamon}
Sift the flour, baking soda, salt and cinnamon together and set aside.
\ing[2]{sticks}{unsalted butter, softened}
\ing[\fr34]{c}{dark brown sugar}
\ing[\fr16]{c}{granulated sugar}
In a medium size mixing bowl, cream the butter with both sugars until
smooth.
\ing[2]{}{eggs}
\ing[2]{tsp}{vanilla extract}
Add the eggs and vanilla, beating until very fluffy. You may use an
electric mixer if desired.
\ing[2\fr34]{c}{whole oats}
\ing[12]{oz}{bittersweet chocolate pieces, or chopped chunk chocolate}
\ing[]{}{sea salt flakes}
Add the sifted ingredients, mixing thoroughly until the batter is
smooth. Add the oats and chocolate, mixing until just blended. Chill
the dough for at least 6 hours.
\freeform
Preheat the oven to 350 degrees. Drop by tablespoonfuls, about 1\fr12
each, on an ungreased baking sheet. Sprinkle with sea salt
flakes. Bake for 13 to 15 minutes. Once finished baking, allow the
cookies to cool for 8 to 10 minutes before transferring to a cooling
rack.
\end{recipe}