\index{Soup!Turkey}
\begin{recipe}{Turkey Soup}{8 servings}{2\fr12 hours}
\freeform This  is Laurie Buss' classic post-Thanksgiving recipe. With leftover turkey, Linda Younkin also prepares a variation of this soup and Turkey Tetrazzini from the Joy of Cooking.
\ing[1]{}{turkey carcass}
\ing[~3]{qts}{chicken broth}
\ing[3]{}{carrots}
\ing[3-4]{stalks}{celery}
\ing[3]{}{bay leaves}
Place the turkey carcass, whole scrubbed carrots, whole rinsed celery stalks and bay leaves in a large pot. Add enough chicken broth to cover the carcass and boil for approximately \unit[45]{minutes} to an hour.
\newstep Remove the carcass and all bones. Strain the remaining solids from the broth and reserve. Pick all of the meat off of the carcass and bones and add back in to the broth.
\ing[3-4]{stalks}{celery}
\ing[28]{oz}{canned plum tomatoes}
Chop the fresh celery and roughly chop the drained tomatoes, adding both back in to the broth. Simmer for 30 minutes.
\ing{}{rice or egg noodles}
If you choose to use rice, add in a cup or a cup and a half at this step and simmer for 20 minutes then serve. If you choose to use noodles, add about two cups of egg noodles, simmering until tender. Season with salt and pepper to taste.
\freeform A turkey carcass should have a reasonable amount of meat remaining on it after the majority has been carved off. You can also chop up and add leftover meat from other pieces at step 2. If you have smoked your turkey, we find it best to remove the skin from the carcass before step 1.
\end{recipe}
